---
title: "Using `cheatR`"
author: "Mattan S. Ben-Shachar"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using `cheatR`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
  # fig.path = "/man/figures/"
)
```

### Scripting

Create a list of files:

```{r}
my_files <- list.files(path = '../man/files/', pattern = '.doc', full.names = TRUE)
my_files
```
The first 3 documents are different drafts of the same paper, so we would expect them to be similar to each other. The last document is a draft of a different paper, so it should be dissimilar to the first 3. **All files are about 45K words long.**

Now we can use `cheatR` to find duplicates.  

The only function, `catch_em`, takes the following input arguments:  
  
  - `flist` - a list of documents (`.doc`/`.docx`/`.pdf`). A full/relative path must be provided.
  - `n_grams` - see [`ngram` package](https://github.com/wrathematics/ngram).
  - `time_lim` - max time in seconds for each comparison (we found that some corrupt files run forever and crash R, so a time limit might be needed).

```{r}
library(cheatR)
results <- catch_em(flist = my_files,
                    n_grams = 10, time_lim = 1) # defaults
```

The resulting list contains a matrix with the similarity values between each pair of documents:

```{r}
results
```

You can also plot the relational graph if you'd like to get a more clear picture of who copied from who.

```{r cheater_graph}
plot(results, weight_range = c(0.7, 1), remove_lonely = FALSE)
```